---
title: "Anxiety and Fear Differ in Construal Level and Scope / Study 1"
output: html_document
editor_options: 
  chunk_output_type: console
---

This R Markdown file present the analysis procedure and results for Study 1 in the project: "Anxiety and Fear Differ in Construal Level and Scope"

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Session info

```{r session info, echo=FALSE}
message(paste("#", capture.output(sessionInfo()), "\n", collapse =""))
# R version 4.1.2 (2021-11-01) 
# Platform: x86_64-w64-mingw32/x64 (64-bit) 
# Running under: Windows 10 x64 (build 19042) 
#  
# Matrix products: default 
#  
# locale: 
# [1] LC_COLLATE=Swedish_Sweden.1252  LC_CTYPE=Swedish_Sweden.1252    LC_MONETARY=Swedish_Sweden.1252 
# [4] LC_NUMERIC=C                    LC_TIME=Swedish_Sweden.1252     
#  
# attached base packages: 
# [1] stats     graphics  grDevices utils     datasets  methods   base      
#  
# other attached packages: 
#  [1] openxlsx_4.2.5  fastmatch_1.1-3 readxl_1.3.1    forcats_0.5.1   stringr_1.4.0   dplyr_1.0.8     
#  [7] purrr_0.3.4     readr_2.1.2     tidyr_1.2.0     tibble_3.1.6    ggplot2_3.3.5   tidyverse_1.3.1 
#   
```

## Preparation: Load packages and dataset

```{r packages, message=FALSE, results='hide', warning=FALSE}
# Required packages
pkgs <- c("tidyverse","readxl","fastmatch","openxlsx","corrplot","readr",
          "ggplot2","cowplot","ggpubr","PupillometryR","rstatix")

# RUn the two lines below to heck to see if packages are installed. Install them if they are not, then load them into the R session.
#new.pkgs <- pkgs[!(pkgs %in% installed.packages()[, "Package"])]

#if (length(new.pkgs)) install.packages(new.pkgs, dependencies = TRUE)

lapply(pkgs, library, character.only = TRUE)

# Import data
df_full <- read.csv(file = "anxiety_abstraction_s1.csv", head = TRUE, sep=";")
```

## The code (developed by Yeomans, 2021) below was used to create the linguistic concreteness index.

```{r, eval=FALSE}
# Load the raw data that contains the text to be analyzed
RawData <- readxl::read_xlsx("anxiety_abstraction_study1_raw.xlsx")

# ==== upload libraries ====
library(tidytext)
library(tidyverse)

# === upload dics ====

load("brysbaert_dic.RData") 
brysbaert_dic$Word<-tolower(brysbaert_dic$Word)

load("bigrams_brysbaert.RData")
bigrams_brysbaert$Word <- tolower(bigrams_brysbaert$Word)

# ==== function: "cleantext" =====
#' @description background function to load.
#' uses background functions: 
#' (1) textformat; (2) ctxpand ; 
#' @param text character Vector of strings to clean.
#' @param language character Language to use for cleaning. Default is "english".
#' @param punct logical Should punctuation be kept as tokens? Default is TRUE.
#' @param stop.words logical Should stop words be kept? default is TRUE.
#' @param number.words logical Should numbers be converted to words? default is TRUE.
#' @return character Vector of cleaned strings.

cleantext<-function(text, language="english", punct=FALSE,
                    stop.words=TRUE, number.words=TRUE){
  
  #PUTS ALL LETTERS IN LOWER CASE
  text<-tolower(text)
  text<-textformat(text, punct)
  
  #EXPANDS CONTRACTIONS
  if(language=="english"){
    text<-ctxpand(text)
  }
  
  #DELETES PUNCTUATION & HTML JUNK
  text<-gsub("[[:punct:]]", " ", text,perl=TRUE)
  
  #DELETES STOP WORDS
  if(length(stop.words)>1){
    text<-tm::removeWords(text, stop.words)
  }else if(!stop.words){
    text<-tm::removeWords(text, tm::stopwords(language))
  }
  
  # NUMBERS CONVERTED TO WORDS
  if(number.words){
    text<-strsplit(text," ")[[1]]
    nx<-suppressWarnings(as.numeric(text))
    
    text[!is.na(nx)]<-as.character(english::as.english(nx[!is.na(nx)]))
    text<-paste(text,collapse=" ")
  } else {  #DELETES NUMBERS
    text<-tm::removeNumbers(text)
  }
  
  text<-tm::stripWhitespace(text) # Strip extra white spaces 
  return(as.character(text))
}

# ==== function: "textformat" =====
#' @description background function to load.
#' @param text character Vector of strings to clean.
#' @param punct logical Should punctuation be kept as tokens? Default is FALSE.
#' @return character Vector of cleaned strings.

textformat<-function(text, punct=FALSE){
  text <- gsub(" ?(f|ht)tp(s?)://(.*)[.][a-z]+", "", text,perl=TRUE)
  text <- gsub("www.(.*)[.][a-z]+", "", text,perl=TRUE)
  text <- gsub("\u201D", "\"", text,perl=TRUE)
  text <- gsub("\u201C", "\"", text,perl=TRUE)
  text <- gsub("\u2019", "\'", text,perl=TRUE)
  
  text<-gsub("ha ha"," haha ",text,fixed=TRUE)
  text<-gsub("lol "," haha ",text,fixed=TRUE)
  text<-gsub("lol."," haha.",text,fixed=TRUE)
  text<-gsub("lol!"," haha!",text,fixed=TRUE)
  text<-gsub("Lol "," haha ",text,fixed=TRUE)
  text<-gsub("Lol."," haha.",text,fixed=TRUE)
  text<-gsub("Lol!"," haha!",text,fixed=TRUE)
  text<-gsub("LOL"," haha ",text,fixed=TRUE)
  text<-gsub("LOl"," haha ",text,fixed=TRUE)
  text<-gsub("LOl"," haha ",text,fixed=TRUE)
  text<-gsub("LoL"," haha ",text,fixed=TRUE)
  text<-gsub("ROFL"," haha ",text,fixed=TRUE)
  text<-gsub("rofl"," haha ",text,fixed=TRUE)
  for (x in 1:8){
    text<-gsub(".?","?",text,fixed=TRUE)
    text<-gsub("?.","?",text,fixed=TRUE)
    text<-gsub("!?","?",text,fixed=TRUE)
    text<-gsub("?!","?",text,fixed=TRUE)
    text<-gsub("??","?",text,fixed=TRUE)
    text<-gsub("!!","!",text,fixed=TRUE)
  }
  if(punct){
    text<-gsub("!"," xmark.",text,fixed=TRUE)
    text<-gsub("?"," qmark.",text,fixed=TRUE)
  }
  text<-gsub("||",". ",text,fixed=TRUE)
  text<-gsub("|",". ",text,fixed=TRUE)
  text<-gsub("[[:cntrl:]]", " ", text,perl=TRUE)
  return(text)
}

# ==== function: "ctxpand" / Contraction Expander ====
#' @description background function to load.
#' @param text character vector of sentences to un-contract.
#' @return character Vector of sentences without contractions.

ctxpand<-function(text){
  text <- gsub("let's", "let us", text, fixed=TRUE)
  text <- gsub("i'm", "i am", text, fixed=TRUE)
  text <- gsub("won't", "will not", text, fixed=TRUE)
  text <- gsub("can't", "cannot", text, fixed=TRUE)
  text <- gsub("Let's", "Let us", text, fixed=TRUE)
  text <- gsub("I'm", "I am", text, fixed=TRUE)
  text <- gsub("Won't", "Will not", text, fixed=TRUE)
  text <- gsub("Can't", "Cannot", text, fixed=TRUE)
  text <- gsub("shan't", "shall not", text, fixed=TRUE)
  text <- gsub("'d", " would", text, fixed=TRUE)
  text <- gsub("'ve", " have", text, fixed=TRUE)
  text <- gsub("'s", " is", text, fixed=TRUE)
  text <- gsub("'ll", " will", text, fixed=TRUE)
  text <- gsub("'re", " are", text, fixed=TRUE)
  text <- gsub("n't", " not", text, fixed=TRUE)
  text <- gsub("u.s.", "US", text, fixed=TRUE)
  text <- gsub("U.S.", "US", text, fixed=TRUE)
  text <- gsub("e.g.", "eg", text, fixed=TRUE)
  text <- gsub("i.e.", "ie", text, fixed=TRUE)
  return(text)
}

# ==== function: "conc_score" ====

conc_score <- function(text, ngrams = T, samp_ave = NULL, stop.words = T, number.words = T){
  #text character object
  #ngrams logic if TRUE include bigrams in computation, if FALSE ignore bigrams 
  #samp_ave integer indicating the sample average of concrete score over participants
  #stop.words and number.words are logistic and belong to clean text function
  
  text <- iconv(textclean::replace_non_ascii(text),to="ASCII",sub=" ") # clean from non ASCII characters
  text[is.na(text) | stringr::str_count(text, "[[:alpha:]]+")==0] <- " . " # clean special characters
  
  # CLEAN TEXT FUNCTION
  ctext <- cleantext(text) # normalize the text before comparing it to the dics
  
  # BIGRAMS
  if (ngrams) {
    bigrams <- data.frame(t = ctext) # make a data frame for tidytext next function
    bigrams <- unnest_tokens(bigrams, input = t, output = Word, token = "ngrams", n = 2) # build bigrams tokens
    
    bigrams <- bigrams %>% left_join(bigrams_brysbaert, by = "Word") # match to dic before lemmatisation
    bigrams$Word[is.na(bigrams$Conc.M)] <- textstem::lemmatize_words(bigrams$Word[is.na(bigrams$Conc.M)]) # lemmatize na's
    
    bigrams <- bigrams %>% select(-Conc.M) %>% left_join(bigrams_brysbaert, by = "Word") %>% drop_na() # match to dic
    
    # REMOVE FOUND BIGRAMS
    if(nrow(bigrams > 0)) {
      ctext <- str_remove_all(ctext, str_c(bigrams$Word ,collapse = "|")) %>% tm::stripWhitespace()}
  }
  else {bigrams <- data.frame()} # empty df for combine allwords
 
  # TEXT WORDS
  words <- data.frame(t = ctext) # make a data frame for tidytext next function
  words <- unnest_tokens(words, input = t, output = Word, token = "words") # build one-word-per-row
  
  words <- words %>% left_join(brysbaert_dic, by = "Word") # match to dic before lemmatisation
  words$Word[is.na(words$Conc.M)] <- textstem::lemmatize_words(words$Word[is.na(words$Conc.M)]) # lemmatize na's
  
  # IF/ELSE: WORDS NOT FOUND IN DIC
  # if not given a sample average, concrete score will be calculated only with words found in dic
  # else words not found in dic will be given the sample average  
  
  if(is.null(samp_ave)){ 
    words <- words %>% select(-Conc.M) %>% left_join(brysbaert_dic, by = "Word") %>% drop_na() # match to dic
  }
  else{
    words <- words %>% select(-Conc.M) %>% left_join(brysbaert_dic, by = "Word") %>% 
      mutate(Conc.M = replace_na(Conc.M, samp_ave)) # match to dic and give sample average
  }
  
  allWords <- rbind(bigrams, words) # combine bigrams with words
  
  conc <- mean(allWords$Conc.M, na.rm = T) # concrete score
  
  return(conc)
}

RawData = RawData %>% rowwise %>%  mutate(concreteness = conc_score(text))

# This datafile which now contains a linguistic abstraction index was imported
# in LIWC to obtain the linguistic mental scope variables (I, They, Future)

RawData$subject <- c(1:nrow(RawData)) # Add subject ID
RawData %>%
 dplyr::select(subject,StartDate,EndDate,
               RecordedDate,"Duration(inseconds)",
               text,"rt_recalltask_Page Submit",
               emotion,failed_instructions,BCI=concreteness,
               abstract,temporal,social,physical,
               hypothetical,fear1:fear3,anxious1:anxious3,
               english,serious,recall,bot_check,
               age,gender) %>%
  write.csv(., file = "study1_BCI.csv", row.names = FALSE)
```

## Preregistered exclusions:
- Spent less than 120 seconds on the entire experiment
- Indicated low English understanding of the experiment (<5 on a 7-point scale)
- Indicated low seriousness in responses (<4 on a 5-point scale)
- Failed instructions in the emotion induction task (coded manually)

```{r exclusions}
# Exclude those who spent less than 2 minutes on the entire survey
df_ex <- df_full %>% filter("Duration(inseconds)" >= 120)

# Exclude those who reported low English understanding
df_ex <- df_ex %>% filter(english >= 5)

# Exclude those who indicated not being serious while filling out the survey
df_ex <- df_ex %>% filter(serious >= 4)

# Exclude those who did not follow instructions in the recall task
df_ex <- df_ex %>% filter(failed_instructions == 0)
```

## Self-reported fear and anxiety

```{r manipulation checks}
# Create fear manipulation check variable
fear_items <- c("fear1","fear2","fear3")
df_ex <- df_ex %>% mutate(mc_fear = rowMeans(
  select(., all_of(fear_items))))

# Create anxiety manipulation check
anxiety_items <- c("anxious1","anxious2","anxious3")
df_ex <- df_ex %>% mutate(mc_anxiety = rowMeans(
  select(., all_of(anxiety_items))))

# Check Cronbach's alphas
## Self-reported fear
df_ex %>%
  select(fear1,fear2,fear3) %>%
  psych::alpha(title = "fear MC")

## Self-reported anxiety
df_ex %>%
  select(anxious1,anxious2,anxious3) %>%
  psych::alpha(title = "anxiety MC")

# Means and SDs
df_ex %>%
  group_by(emotion) %>%
  summarise_at(vars(mc_fear,mc_anxiety),
               list(mean=mean, sd=sd))

# Independent samples t test for self-reported fear
t.test_fear <- df_ex %>%
  rstatix::t_test(mc_fear ~ emotion,
                  var.equal = TRUE,
                  detailed = TRUE) %>% 
  rstatix::add_significance()

t.test_fear

## effect size and CIs
psych::cohen.d(df_ex$mc_fear,
               df_ex$emotion,
               alpha=.05,
               std=TRUE,
               sort=NULL,
               dictionary=NULL,
               MD=TRUE,
               data=NULL)

# Independent samples t test for self-reported anxiety
t.test_anxiety <- df_ex %>%
  rstatix::t_test(mc_anxiety ~ emotion,
                  var.equal = TRUE,
                  detailed = T) %>% 
  rstatix::add_significance()

t.test_anxiety

## effect size and CIs
psych::cohen.d(df_ex$mc_anxiety,
               df_ex$emotion,
               alpha=.05,
               std=TRUE,
               sort=NULL,
               dictionary=NULL,
               MD=TRUE,
               data=NULL)

# Independent samples t test for recall ability
t.test_recall <- df_ex %>%
  rstatix::t_test(recall ~ emotion,
                  var.equal = TRUE,
                  detailed = T) %>% 
  rstatix::add_significance()

t.test_recall

## effect size and CIs
psych::cohen.d(df_ex$recall,
               df_ex$emotion,
               alpha=.05,
               std=TRUE,
               sort=NULL,
               dictionary=NULL,
               MD=TRUE,
               data=NULL)
```

## Hypothesis testing

```{r hypothesis testing}

#### ABSTRACTION ####

## Means and SDs of the two abstraction measures
df_ex %>%
  group_by(emotion) %>%
  summarise_at(vars(BCI, abstract),
               list(mean=mean, sd=sd))

# Linguistic abstraction

## Independent samples t test for BCI
t.test_BCI <- df_ex %>%
  rstatix::t_test(BCI ~ emotion,
                  var.equal = TRUE,
                  alternative = "greater",
                  conf.level = 0.90,
                  p.adjust.method = "holm",
                  paired = FALSE,
                  detailed = T) %>% 
  rstatix::add_significance()

t.test_BCI

## Effect size and CI 
psych::cohen.d(df_ex$BCI,
               df_ex$emotion,
               alpha=.10,
               std=TRUE,
               sort=NULL,
               dictionary=NULL,
               MD=TRUE,
               data=NULL)

## Independent samples t test for self-reported abstraction
t.test_abstract <- df_ex %>%
  rstatix::t_test(abstract ~ emotion,
                  var.equal = TRUE,
                  alternative = "less",
                  conf.level = 0.90,
                  p.adjust.method = "holm",
                  paired = FALSE,
                  detailed = T) %>% 
  rstatix::add_significance()

t.test_abstract

## Effect size and CI 
psych::cohen.d(df_ex$abstract,
               df_ex$emotion,
               alpha=.10,
               std=TRUE,
               sort=NULL,
               dictionary=NULL,
               MD=TRUE,
               data=NULL)

#### PSYCHOLOGICAL DISTANCE ###

## Means and SDs of the self-reported psych distance variables
df_ex %>%
  group_by(emotion) %>%
  summarise_at(vars(temporal,social,physical,hypothetical),
               list(mean=mean, sd=sd))

## Independent samples t test for self-reported temporal distance
t.test_temporal <- df_ex %>%
  rstatix::t_test(temporal ~ emotion,
                  var.equal = TRUE,
                  alternative = "less",
                  conf.level = 0.90,
                  p.adjust.method = "holm",
                  paired = FALSE,
                  detailed = T) %>% 
  rstatix::add_significance()

t.test_temporal

## Effect size and CI 
psych::cohen.d(df_ex$temporal,
               df_ex$emotion,
               alpha=.10,
               std=TRUE,
               sort=NULL,
               dictionary=NULL,
               MD=TRUE,
               data=NULL)

## Independent samples t test for self-reported social distance
t.test_social <- df_ex %>%
  rstatix::t_test(social ~ emotion,
                  var.equal = TRUE,
                  alternative = "less",
                  conf.level = 0.90,
                  p.adjust.method = "holm",
                  paired = FALSE,
                  detailed = T) %>% 
  rstatix::add_significance()

t.test_social

## Effect size and CI
psych::cohen.d(df_ex$social,
               df_ex$emotion,
               alpha=.10,
               std=TRUE,
               sort=NULL,
               dictionary=NULL,
               MD=TRUE,
               data=NULL)

## Independent samples t test for self-reported physical distance
t.test_physical <- df_ex %>%
  rstatix::t_test(physical ~ emotion,
                  var.equal = TRUE,
                  alternative = "less",
                  conf.level = 0.90,
                  p.adjust.method = "holm",
                  paired = FALSE,
                  detailed = T) %>% 
  rstatix::add_significance()

t.test_physical

## Effect size and CI
psych::cohen.d(df_ex$physical,
               df_ex$emotion,
               alpha=.10,
               std=TRUE,
               sort=NULL,
               dictionary=NULL,
               MD=TRUE,
               data=NULL)

## Independent samples t test for self-reported hypotheticality 
t.test_hypothetical <- df_ex %>%
  rstatix::t_test(hypothetical ~ emotion,
                  var.equal = TRUE,
                  alternative = "less",
                  conf.level = 0.9,
                  p.adjust.method = "holm",
                  paired = FALSE,
                  detailed = T) %>% 
  rstatix::add_significance()

t.test_hypothetical

## Effect size and CI
psych::cohen.d(df_ex$hypothetical,
               df_ex$emotion,
               alpha=.10,
               std=TRUE,
               sort=NULL,
               dictionary=NULL,
               MD=TRUE,
               data=NULL)

## Means and SDs of the linguistic scope variables
df_ex %>%
  group_by(emotion) %>%
  summarise_at(vars(i,they,focusfuture),
               list(mean=mean, sd=sd))

## Independent samples t test for linguistic scope ("I")
t.test_i <- df_ex %>%
  rstatix::t_test(i ~ emotion,
                  var.equal = TRUE,
                  alternative = "greater",
                  conf.level = 0.90,
                  p.adjust.method = "holm",
                  paired = FALSE,
                  detailed = T) %>% 
  rstatix::add_significance()

t.test_i

## Effect size and CI
psych::cohen.d(df_ex$i,
               df_ex$emotion,
               alpha=.10,
               std=TRUE,
               sort=NULL,
               dictionary=NULL,
               MD=TRUE,
               data=NULL)

## Independent samples t test for linguistic scope ("They")
t.test_they <- df_ex %>%
  rstatix::t_test(they ~ emotion,
                  var.equal = TRUE,
                  alternative = "less",
                  conf.level = 0.90,
                  p.adjust.method = "holm",
                  paired = FALSE,
                  detailed = T) %>% 
  rstatix::add_significance()

t.test_they

## Effect size and CI
psych::cohen.d(df_ex$they,
               df_ex$emotion,
               alpha=.10,
               std=TRUE,
               sort=NULL,
               dictionary=NULL,
               MD=TRUE,
               data=NULL)

## Independent samples t test for linguistic scope ("focusfuture)
t.test_future <- df_ex %>%
  rstatix::t_test(focusfuture ~ emotion,
                  var.equal = TRUE,
                  alternative = "less",
                  conf.level = 0.90,
                  p.adjust.method = "holm",
                  paired = FALSE,
                  detailed = T) %>% 
  rstatix::add_significance()

t.test_future

## Effect size and CI
psych::cohen.d(df_ex$focusfuture,
               df_ex$emotion,
               alpha=.10,
               std=TRUE,
               sort=NULL,
               dictionary=NULL,
               MD=TRUE,
               data=NULL)
```

## Correlations

```{r correlations}
 corr_df <- df_ex %>%
   dplyr::select(emotion,BCI,abstract,temporal,social,
                 physical,hypothetical)

 corr_df$emotion <- as.numeric(corr_df$emotion)

# Run code chunk below to create correlation table (remove hashtags)
  apaTables::apa.cor.table(
  corr_df,
  #filename = "study1_corrtable.doc",
  show.conf.interval = TRUE,
  show.sig.stars = TRUE,
  landscape = TRUE
)

# Obtain the p-values of correlations
Hmisc::rcorr(as.matrix(corr_df),type="pearson")

# Plot correlations
 M = cor(corr_df)

 testRes = cor.mtest(corr_df, conf.level = 0.95)

 corrplot(M, p.mat = testRes$p,
          diag = FALSE,
          type = 'upper',
          sig.level = c(0.001, 0.01, 0.05, 0.1),
          pch.cex = 0.9,
          insig = 'label_sig',
          tl.col="black")
```

## Raincloud plots

```{r raincloud, warning=FALSE}
df_ex <- df_ex %>% 
  dplyr::select(emotion,abstract,BCI,temporal,social,
                physical,hypothetical)

df_ex$emotion <- df_ex$emotion %>%
  factor(levels = c(0, 1), labels = c("Fear","Anxiety"))

# Raincloud plot: perceived threat abstractness 
df_sum1 <- df_ex %>%
  group_by(emotion) %>%
  summarise( 
    n=n(),
    mean=mean(abstract),
    sd=sd(abstract)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ci=se * qt((1-0.05)/2 + .5, n-1))

raincloud1 <- ggplot(df_ex, aes(x = emotion,
                          y = abstract,
                          fill = emotion)) +
  geom_flat_violin(aes(fill = emotion),
                   position = position_nudge(x = .1, y = 1),
                   adjust = 1, trim = FALSE,
                   alpha = .5, colour = NA) +
  geom_point(aes(x = as.numeric(emotion)-.15,
                 y = abstract, colour = emotion),
             position = position_jitter(width = .05),
             size = 1,
             shape = 20) +
  geom_boxplot(aes(x = emotion,
                   y = abstract,
                   fill = emotion),
               outlier.shape = NA,
               alpha = .5,
               width = .1,
               colour = "black") +
  scale_colour_brewer(palette = "Set2") +
  scale_fill_brewer(palette = "Set2") +
  labs(y= "Perceived threat abstractness") +
  theme_cowplot(font_size = 14, font_family = "serif") +
  theme(legend.position = "none") +
  theme(axis.title.x = element_blank()) +
  scale_y_continuous(labels = scales::label_number(accuracy = 1),
                     limits = c(0,9))+
  geom_errorbar(data = df_sum1,
                aes(x = as.numeric(emotion)-.002,
                    y = mean,
                    group = emotion,
                    ymin = mean-ci,
                    ymax = mean+ci),
                width = .05) +
  stat_summary(fun="mean",
               colour="grey",
               geom="line",
               aes(group = 1)) +
    geom_point(stat="summary",
             fun="mean",
             size=2)

raincloud1

# Raincloud plot 2: physical distance 
df_sum2 <- df_ex %>%
  group_by(emotion) %>%
  summarise( 
    n=n(),
    mean=mean(physical),
    sd=sd(physical)
  ) %>%
  mutate(se=sd/sqrt(n))  %>%
  mutate(ci=se * qt((1-0.05)/2 + .5, n-1))

raincloud2 <- ggplot(df_ex, aes(x = emotion,
                          y = physical,
                          fill = emotion)) +
  geom_flat_violin(aes(fill = emotion),
                   position = position_nudge(x = .1, y = 1),
                   adjust = 1, trim = FALSE,
                   alpha = .5, colour = NA) +
  geom_point(aes(x = as.numeric(emotion)-.15,
                 y = physical, colour = emotion),
             position = position_jitter(width = .05),
             size = 1,
             shape = 20) +
  geom_boxplot(aes(x = emotion,
                   y = physical,
                   fill = emotion),
               outlier.shape = NA,
               alpha = .5,
               width = .1,
               colour = "black") +
  scale_colour_brewer(palette = "Set2") +
  scale_fill_brewer(palette = "Set2") +
  labs(y= "Physical distance of threat") +
  theme_cowplot(font_size = 14, font_family = "serif") +
  theme(legend.position = "none") +
  theme(axis.title.x = element_blank()) +
  scale_y_continuous(labels = scales::label_number(accuracy = 1),
                     limits = c(0,7))+
  geom_errorbar(data = df_sum2,
                aes(x = as.numeric(emotion)-.002,
                    y = mean,
                    group = emotion,
                    ymin = mean-ci,
                    ymax = mean+ci),
                width = .05) +
  stat_summary(fun="mean",
               colour="grey",
               geom="line",
               aes(group = 1)) +
    geom_point(stat="summary",
             fun="mean",
             size=2)

# Raincloud plot 3: hypotheticality 
df_sum3 <- df_ex %>%
  group_by(emotion) %>%
  summarise( 
    n=n(),
    mean=mean(hypothetical),
    sd=sd(hypothetical)
  ) %>%
  mutate(se=sd/sqrt(n))  %>%
  mutate(ci=se * qt((1-0.05)/2 + .5, n-1))

raincloud3 <- ggplot(df_ex, aes(x = emotion,
                          y = hypothetical,
                          fill = emotion)) +
  geom_flat_violin(aes(fill = emotion),
                   position = position_nudge(x = .1, y = 1),
                   adjust = 1, trim = FALSE,
                   alpha = .5, colour = NA) +
  geom_point(aes(x = as.numeric(emotion)-.15,
                 y = hypothetical, colour = emotion),
             position = position_jitter(width = .05),
             size = 1,
             shape = 20) +
  geom_boxplot(aes(x = emotion,
                   y = hypothetical,
                   fill = emotion),
               outlier.shape = NA,
               alpha = .5,
               width = .1,
               colour = "black") +
  scale_colour_brewer(palette = "Set2") +
  scale_fill_brewer(palette = "Set2") +
  labs(y= "Hypotheticality of threat") +
  theme_cowplot(font_size = 14, font_family = "serif") +
  theme(legend.position = "none") +
  theme(axis.title.x = element_blank()) +
  scale_y_continuous(labels = scales::label_number(accuracy = 1),
                     limits = c(0,7))+
  geom_errorbar(data = df_sum3,
                aes(x = as.numeric(emotion)-.002,
                    y = mean,
                    group = emotion,
                    ymin = mean-ci,
                    ymax = mean+ci),
                width = .05) +
  stat_summary(fun="mean",
               colour="grey",
               geom="line",
               aes(group = 1)) +
    geom_point(stat="summary",
             fun="mean",
             size=2)

# Raincloud plot 4: social distance
df_sum4 <- df_ex %>%
  group_by(emotion) %>%
  summarise( 
    n=n(),
    mean=mean(social),
    sd=sd(social)
  ) %>%
  mutate(se=sd/sqrt(n))  %>%
  mutate(ci=se * qt((1-0.05)/2 + .5, n-1))

raincloud4 <- ggplot(df_ex, aes(x = emotion,
                          y = social,
                          fill = emotion)) +
  geom_flat_violin(aes(fill = emotion),
                   position = position_nudge(x = .1, y = 1),
                   adjust = 1, trim = FALSE,
                   alpha = .5, colour = NA) +
  geom_point(aes(x = as.numeric(emotion)-.15,
                 y = social, colour = emotion),
             position = position_jitter(width = .05),
             size = 1,
             shape = 20) +
  geom_boxplot(aes(x = emotion,
                   y = social,
                   fill = emotion),
               outlier.shape = NA,
               alpha = .5,
               width = .1,
               colour = "black") +
  scale_colour_brewer(palette = "Set2") +
  scale_fill_brewer(palette = "Set2") +
  labs(y= "Social distance of threat") +
  theme_cowplot(font_size = 14, font_family = "serif") +
  theme(legend.position = "none") +
  theme(axis.title.x = element_blank()) +
  scale_y_continuous(labels = scales::label_number(accuracy = 1),
                     limits = c(0,7))+
  geom_errorbar(data = df_sum4,
                aes(x = as.numeric(emotion)-.002,
                    y = mean,
                    group = emotion,
                    ymin = mean-ci,
                    ymax = mean+ci),
                width = .05) +
  stat_summary(fun="mean",
               colour="grey",
               geom="line",
               aes(group = 1)) +
    geom_point(stat="summary",
             fun="mean",
             size=2)

# Raincloud plot 5: temporal distance
df_sum5 <- df_ex %>%
  group_by(emotion) %>%
  summarise( 
    n=n(),
    mean=mean(temporal),
    sd=sd(temporal)
  ) %>%
  mutate(se=sd/sqrt(n))  %>%
  mutate(ci=se * qt((1-0.05)/2 + .5, n-1))

raincloud5 <- ggplot(df_ex, aes(x = emotion,
                          y = temporal,
                          fill = emotion)) +
  geom_flat_violin(aes(fill = emotion),
                   position = position_nudge(x = .1, y = 1),
                   adjust = 1, trim = FALSE,
                   alpha = .5, colour = NA) +
  geom_point(aes(x = as.numeric(emotion)-.15,
                 y = temporal, colour = emotion),
             position = position_jitter(width = .05),
             size = 1,
             shape = 20) +
  geom_boxplot(aes(x = emotion,
                   y = temporal,
                   fill = emotion),
               outlier.shape = NA,
               alpha = .5,
               width = .1,
               colour = "black") +
  scale_colour_brewer(palette = "Set2") +
  scale_fill_brewer(palette = "Set2") +
  labs(y= "Temporal distance of threat") +
  theme_cowplot(font_size = 14, font_family = "serif") +
  theme(legend.position = "none") +
  theme(axis.title.x = element_blank()) +
  scale_y_continuous(labels = scales::label_number(accuracy = 1),
                     limits = c(0,7))+
  geom_errorbar(data = df_sum5,
                aes(x = as.numeric(emotion)-.002,
                    y = mean,
                    group = emotion,
                    ymin = mean-ci,
                    ymax = mean+ci),
                width = .05) +
  stat_summary(fun="mean",
               colour="grey",
               geom="line",
               aes(group = 1)) +
    geom_point(stat="summary",
             fun="mean",
             size=2)

ggpubr::ggarrange(raincloud2,raincloud3,raincloud4,raincloud5)
```
